An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-03-05 poly-embed-journal/poly-embed-journal.tex
Pass on examples section for top k and WW

\begin{figure}
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{figs/0-1-br.pdf}
%		\caption{Bayes risk of the 0-1 loss.}
%		\label{fig:0-1-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering		\includegraphics[width=0.95\linewidth]{figs/hinge-br.pdf}
%		\caption{Bayes risk of hinge loss.}
%		\label{fig:hinge-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{figs/logistic-br.pdf}
%	\caption{Bayes risk of the logistic loss.}
%	\label{fig:logistic-br}
\end{minipage}
\caption{Bayes risks $L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = Pr[Y=1]$.
	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.  \raf{Add detail}\jessie{better?}\raf{Take a step back and ask: what point do we (want to) make with this figure? Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}}
\label{fig:bayes-risks-01}
\end{figure}

@@

Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete loss.
This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss it embeds.
Below, we illustrate the power of this framework with specific examples from the literature.
To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
We then give three examples of subsequent works that use our framework to study existing surrogates, and derive new ones using Theorem~\ref{thm:discrete-loss-poly-embeddable}.

When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To this end, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh this sentence feels like a lie lol}
Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
From here one can further remove redundant reports until one arrives at a tight embedding if desired.
Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem (\S~\ref{sec:winge}, \ref{sec:top-k}).
Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}).
\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}

@@

Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
In particular, \citet{ramaswamy2018consistent} study the loss $\ell^{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ell^{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
\end{equation}
where $\varphi$ embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$. %\raft{Double-check theorem ref; was eps-thick-calibrated.  Also below.}.
Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
\begin{equation}\label{eq:abstain-link-1}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^\alpha$.
Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.
\citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}, and that $\psi$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.

% \jessiet{Clarified, but also think it's fine to remove the paragraph}
\raft{Commented out hierarchical paragraph for now :-)}
% The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
% Given a tree $H = ([n], E,W)$ defined by a finite class of labels $[n]$, edges $E$, and weights $W$, they consider the discrete loss 
% \begin{equation}\label{eq:tree-loss-discrete}
% 	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
% \end{equation}
% The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
% We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}. 
% \raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}
% \jessiet{They sequentially apply the BEP surrogate on each level of the tree (start at the root; if you predict on a child, move to that child.  If you abstain, stay at the current node), It would be a mess to apply and probably to describe, which moves me in even stronger favor of deleting this paragraph.}

\begin{figure}
\begin{center}
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-linf.pdf}
\end{minipage}\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-U-regions-l1.pdf}
\end{minipage}\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-l1.pdf}
\end{minipage}\hfill
\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$. The embedding is shown in bold labeled by the corresponding reports. (L) The link envelope $\Psi$ resulting from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.  (M) An illustration of the thickened sets from Construction~\ref{const:eps-thick-link} for two sets $U \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$. (R) The $\Psi$ and $\psi$ from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_1$ and $\epsilon = 1$.}
\label{fig:abstain-links}
\end{center}
\end{figure}

@@

\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular and $L^f$ reduces to weighted Hamming loss.
Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
To derive $\ellabs$, they show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\ellabs := L^f|_{\V}$.
Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
\begin{equation}
	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
\end{equation}
(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
Thus, interestingly, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.

\jessie{TODO: add a bit about the link construction}

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L_{WW}(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.

\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_k) \mid k \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
\end{align*}

@@

The ordered partition loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link.
\jessie{Natural link to test is a rounding link, yeah?}
\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1?}

@@

\begin{definition}[Supports]
	A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	% (i) $P \subseteq H^+$ for a halfspace $H^+$ corresponding to $H$
	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$
	(ii)$H \cap \partial P \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \partial P$.
\end{definition}

\jessie{In definition 19, need a way to go uniquely from halfspace to hyperplane}

>>>>

\begin{figure}
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{figs/0-1-br.pdf}
%		\caption{Bayes risk of the 0-1 loss.}
%		\label{fig:0-1-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering		\includegraphics[width=0.95\linewidth]{figs/hinge-br.pdf}
%		\caption{Bayes risk of hinge loss.}
%		\label{fig:hinge-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{figs/logistic-br.pdf}
%	\caption{Bayes risk of the logistic loss.}
%	\label{fig:logistic-br}
\end{minipage}
\caption{Bayes risks $\risk L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = Pr[Y=1]$.
	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise lienar and concave, while the Bayes risk of logistic loss is also concave, but not piecewise linear.  Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks.
	This confirms that hinge loss (M) embeds 0-1 loss (L), while logistic loss  (R) does not. \raf{Add detail}\jessie{better?}\raf{Take a step back and ask: what point do we (want to) make with this figure? Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}}
\label{fig:bayes-risks-01}
\end{figure}

@@

Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete loss.
This framework also provides a way to verify the consistency or inconsistency of a given polyhedral surrogate, by first determining the discrete loss $\ell_{\mathrm{embed}}$ it embeds and comparing $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
Below, we illustrate the power of this framework with specific examples from the literature.
To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, and show how to rederive their link function using Theorem~\ref{thm:link-main}.
We then give three examples of subsequent works that use our framework to study existing surrogates for proposed target losses or derive calibrated polyhedral surrogates for the proposed target via Theorem~\ref{thm:discrete-loss-poly-embeddable}.

When using our framework to study an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To this end, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function (\S~\ref{sec:lovasz-hinge}, \ref{sec:top-k}).
Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
From here one can further remove redundant reports until one arrives at a tight embedding if desired.
Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on conditional label distributions is it consistent for the original problem (\S~\ref{sec:winge}, \ref{sec:top-k}).
Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
A key step in Construction~\ref{const:eps-thick-link} is constructing the link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:lovasz-hinge}, \ref{sec:top-k}).
\raft{We should discuss this a bit in the examples where appropriate, e.g. WW, and then forward ref in parens here to the relevant subsection(s)}

@@

Several authors consider a variant of classification, with the addition of a reject or \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
In particular, \citet{ramaswamy2018consistent} study the loss $\ell^{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell^{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' if no one label is sufficiently likely: specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L_\alpha$ for $\ell^{\alpha}$ when $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
\end{equation}
where $\varphi$ embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$. 
Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
\begin{equation}\label{eq:abstain-link-1}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ell^\alpha$. \jessie{does it?  do we know $\epsilon$ is small enough for higher $d$?}
Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right?}.

\citeauthor{ourlovaszpaper} observe that the BEP surrogate $L_{1/2}$ in eq.~\eqref{eq:abstain-surrogate} is one example of a Lov\'asz hinge introduced in \S~\ref{sec:lovasz-hinge}, and that $\psi$ in eq.~\eqref{eq:abstain-link} is an example of a calibrated link given by Construction~\ref{const:eps-thick-link} for the embedded loss.

\begin{figure}
\begin{center}
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-linf.pdf}
\end{minipage}\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-U-regions-l1.pdf}
\end{minipage}\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=\linewidth]{tikz/abstain-link-l1.pdf}
\end{minipage}\hfill
\caption{Constructing links for the abstain surrogate $L_{1/2}$ with $d=2$. The embedding is shown in bold labeled by the corresponding reports. (L) The link envelope $\Psi$ resulting from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_\infty$ and $\epsilon = 1/2$, and a possible link $\psi$ which matches eq.~\eqref{eq:abstain-link} from~\cite{ramaswamy2018consistent}.  (M) An illustration of the thickened sets from Construction~\ref{const:eps-thick-link} for two sets $U, U' \in \U$, using $\|\cdot\|_1$ and $\epsilon = 1$. (R) The $\Psi$ and $\psi$ from Construction~\ref{const:eps-thick-link} using $\|\cdot\|_1$ and $\epsilon = 1$.}
\label{fig:abstain-links}
\end{center}
\end{figure}

@@

\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular and $\ell^f$ is weighted Hamming loss.
Moreover, they show what $L^f$ embeds: a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $S \subseteq [k]$, which they call the \emph{structured abstain problem}.
To derive $\ellabs$, they show that the set $\V = \{-1,0,1\}^k$ is representative for $L^f$, and use our Proposition~\ref{prop:representative-embeds-restriction} to show that $L^f$ embeds $\ellabs := L^f|_{\V}$.
Letting $\abs(v) = \{i\in[k] \mid v_i = 0\}$ denote the ``abstain'' set, we may write $\ellabs : \V \to \reals^\Y_+$ as
\begin{equation}
	\ellabs(v)_y = f(\dis(v,y) \setminus \abs(v)) + f(\dis(v,y))~.
\end{equation}
(Observe that $\abs(v,y) \subseteq \dis(v,y)$, since $y\in\{-1,1\}^k$.)
%They go on to show that the embedding is tight, for $f$ strictly submodular and strictly monotone, if one first disallows $v$ with $|\abs(v)| = 1$.
Thus, interestingly, the Lov\'asz hinge is consistent with respect to the structured abstain loss $\ellabs$.

\jessie{new: added a bit about links. not sure how I feel about it yet.}
Since $L^f$ embeds $\ellabs$, Theorem~\ref{thm:link-main} implies that, for each submodular and increasing $f : 2^{[k]} \to \reals_+$, there exists a link $\psi^f$ such that $(L^f, \psi^f)$ is calibrated with respect to $\ellabs$.
Perhaps surprisingly, \citeauthor{ourlovaszpaper} find two links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $(L^f, \psi^\diamond)$ are both calibrated with respect to $\ellabs$, regardless of $f$.
These links are visualized for $k = 2$ in Figure~\ref{fig:lovasz-links}.

\begin{figure}
	\begin{center}
		\begin{minipage}{0.48\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.48\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
		\end{minipage}\hfill
		\caption{Links $\psi^*$ and $\psi^\diamond$ such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$. Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?  Would we just be better off explicitly labeling things?}}
		\label{fig:lovasz-links}
	\end{center}
\end{figure}

\subsection{Inconsistency of previous top-$k$ losses, constructing a calibrated top-$k$ surrogate via embeddings, and verifying a canonical link}
\label{sec:top-k}
In settings like object recognition and information retrieval, the top-$k$ classification problem arises in which one predicts a set $S$ of size $k$, and if the true outcome is $y$, receives loss $\elltopk(S)_y = \ones\{y\notin S\}$~\citep{lapin2015top, lapin2016loss, lapin2018analysis,yang2018consistency,berrada2018smooth,rastegari2011scalable,reddi2019stochastic}.
Many of the existing surrogates for top-$k$ classification consider the following three desiderata: convexity, calibration, and piecewise linear (``hinge-like'') structure.
Satisfying all three desiderata simultaneously had not been observed until their work.
The surrogates that are convex and calibrated but not polyhedral often elicit the entire distribution $p \in \simplex$, and take the link to be the top $k$ elements of $p$, as noted by~\citep{lapin2016loss}, which learns more information than desired and seems to require more samples to converge.\jessie{fact check; cite rates paper?}
\citet{yang2018consistency} propose a piecewise linear surrogate that is calibrated for top-$k$ classification, but is not convex, generally making optimization more difficult.
Now consider the class of polyhedral surrogates whose calibration for top-$k$ is unknown~\citep{yang2018consistency,lapin2016loss}: Theorem~\ref{thm:poly-embeds-discrete} says that every polyhedral surrogate embeds some discrete loss, and Theorem~\ref{thm:embed-poly-main} states that embedding implies calibration by some link for this discrete loss; thus, we can use embedding to analyze the (non)calibration of existing polyhedral surrogates with respect to top-$k$ by comparing the embedded losses to top-$k$.

\citet{finocchiaro2022consistenttopk} apply the embedding framework to these surrogates to understand the target problems for which they are consistent.
%$\psi_3$ from~\citet[Table 1]{yang2018consistency} elicits a similar property to $\prop{\ell^\OP}$ shown in Figure~\ref{fig:ordered-partition}, but it is proposed as a surrogate for a different task. \jessiet{Do we even want this sentence?}
\citeauthor{finocchiaro2022consistenttopk} consider the polyhedral surrogates proposed by \citet[Table 1, cf. $\psi_2, \psi_3, \psi_4$]{yang2018consistency} and evaluate \emph{which discrete losses these surrogates embed}, if not top-$k$.
None of the studied surrogates embed top-$k$ but use the properties elicited by the embedded losses to characterize (tighter\jessie{not sure how to say this.  better bounds than YK gave, which was just the abstain cell for all the surrogates}) sufficient assumptions on the data distribution in order be calibrated with respect to top-$k$, fixing the link to be the canonical argmax link $\psi^k$.
\jessie{do we want to drop the table here or nah?}

Moreover, \citeauthor{finocchiaro2022consistenttopk} uses Theorem~\ref{thm:discrete-loss-poly-embeddable} to derive the first calibrated polyhedral surrogate for $\elltopk$, given in eq.~\eqref{eq:topk-embedding}.
Here $u_{[i]}$ denotes the $i^{th}$ largest element of $u \in \reals^n$.
\begin{align}\label{eq:topk-embedding}
L^k(u)_y &= \max \left(u_{[1]}, \max_{m \in \{k+1, \ldots, m\}} \left[ 1 - \frac k m + \frac 1 m \sum_{i=1}^m u_{[i]}\right] \right)- u_y~.
\end{align}
While Theorem~\ref{thm:link-main} guarantees the existence of a link function from $L^k$ to $\elltopk$, we ideally would like to use the intuitive argmax link function 
$\psi^k(u)$ which returns the $k$ largest elements of $u$ (breaking ties arbitrarily).
\citeauthor{finocchiaro2022consistenttopk} Theorem 4.4 confirms that indeed $(L^k,\psi^k)$ is calibrated with respect to $\elltopk$ for this link $\psi^k$, by showing that $\psi^k$ is an $\epsilon$-separated link for $\elltopk$ with any $\epsilon < \frac 1 {2n}$ via the construction of the link envelope $\Psi$ in Construction~\ref{const:eps-thick-link}.
See Figure~\ref{fig:top-k} for the properties elicited by the embedded losses for previous surrogates~\citep{lapin2016loss,yang2018consistency}, and how they compare to $\prop{\elltopk}$ with $n = 3$ and $k = 2$.
%In order to verify calibration of the canonical link they verify, for all $u \in \reals^n$, the proposed $\psi(u) \in \Psi(u)$, and thus yields an $\epsilon$-separated link.

\begin{figure}
	\begin{center}
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/top-k-L2.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/top-k-L4.pdf}
		\end{minipage}\hfill
		\caption{The properties elicited by previous polyhedral surrogates ($\psi_2, \psi_3, \psi_4$ in \citep[Table 1]{yang2018consistency}, respecitvely) with $n = 3, k = 2$. 
		The dashed lines in each simplex denote $\prop{\elltopk}$, and blue regions represent cells where the top-$k$ elements of $\prop{L}$ are ambiguous, and therefore calibration cannot be guaranteed by the argmax link $\psi^k$.
		In this setting, the third surrogate is calibrated via $\psi^k$ with respect to $\elltopk$, though this does not hold for general $k,n$.
		\jessie{revisit}}
		\label{fig:top-k}
	\end{center}
\end{figure}

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L_{WW}(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems. \jessie{do we want the ponit about dogan et al or do we not care?}

\citet*{wang2020weston} use the embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, recover the result of inconsistency with respect to 0-1 loss.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_k) \mid k \geq 1, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
\end{align*}
\jessie{do we want $k$ or something else, given the previous section?}

@@

The ordered partition loss can be interpreted as a variation of 0-1 loss incorporating varying confidence in different outcomes: reports are a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all earlier sets.
\citet{wang2020weston} show that $L_{WW}$ embeds $\ell^\OP$, with the embedding
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
\citeauthor{wang2020weston} then apply Theorem~\ref{thm:link-main} to conclude that there exists a link function $\psi$ such that $(L_{WW},\psi)$ is calibrated with respect to $\ell^\OP$; however, they do not construct the link. \jessie{want to omit this detail?}
Figure~\ref{fig:ordered-partition} gives the cells $\{p \in \simplex \mid T \in \prop{L_{WW}}(p)\}$ for each $T \in \T$, outlined in solid black.
These cells are juxtaposed with the cells $\{p \in \simplex \mid T \in \mode(p)\}$, outlined in dashed blue, for which $L_{WW}$ is proposed as a surrogate.
\jessie{do we want more detail or save it for the caption/the top-$k$ seciton above?}
\raf{Jessie, could you add something here about the figure and dotted lines, which show conditions under which WW is consistent for 0-1? \jessie{\#burn ?}}

@@

\begin{definition}[Supports]
	A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	% (i) $P \subseteq H^+$ for a halfspace $H^+$ corresponding to $H$
	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$, and
	(ii)$H \cap \partial P \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \partial P$.
\end{definition}
